R Markdown for Reproducible Research

### 2019-01-25 paper.Rmd
add stylistic fixes

If Markdown is a lightweight markup language and text formatting syntax, R
Markdown must be Markdown plus R code, right? Yes, with a catch. R Markdown
actually supports _many_ programming languages and output types. It got its
start with R, and R is the primary language engine, but R is an interface
language. This means that R has been (from its outset) commonly used to "wrap"
or call other programming languages. This began as Fortran and C, but has
expanded to include C++, Python, JavaScript, SQL, Stan, and more. As a result, R
Markdown supports the inclusion of many of these programming languages.

@@

It is worth noting that this output can be **problematic for reproducibility**,
though, since you may have unknowingly persisted an output (state) that is no
longer relevant or reproducible.

@@

This process is tedious and error prone: 
 - moving the results to another medium (e.g. from script output to a PowerPoint)
 - copying values, data, plots, images, etc.
 - injecting values into prose (e.g. There are 45 rows in this dataset)

@@

This problem and solution can be reduced to a paradigm of _best practices_ in
which reproducible, data-driven research is greatly simplified by R Markdown.
There are many [much more thorough](https://rpubs.com/marschmi/105639) articles
on the topic, but we will focus on the highlights.

@@

We like to think that the sky is the limit when it comes to the reproducible
results that can be achieved using R Markdown, and are always excited to see
the very cool things that the open source community builds using this tool.

@@

Since our research in this workflow is entirely driven by data along the highway
of code, it makes sense to spend some time getting used to these tools. If we
make version control a part of our process, we get reproducible research up to a
moment in time and easy auditability of code differences since R Markdown
consists of plaintext documents that are easily compared over time.

>>>>

If Markdown is a lightweight markup language and text formatting syntax, R
Markdown must be Markdown plus R code, right? Yes, with a catch. R Markdown
actually supports _many_ programming languages and output types. It got its
start with R, and R is the primary language engine. However, R is an interface
language. This means that R has been (from its outset) commonly used to "wrap"
or call other programming languages. This began as Fortran and C, but has
expanded to include C++, Python, JavaScript, SQL, Stan, and more. As a result, R
Markdown supports the inclusion of many of these programming languages.

@@

It is worth noting that this output can be **problematic for reproducibility.**
Because output is cached, there is _state_ introduced that might unknowingly
persist when it is no longer relevant or reproducible.

@@

This process is tedious and error prone:

 - moving the results to another medium (e.g. from script output to a PowerPoint)
 - copying values, data, plots, images, etc.
 - injecting values into prose (e.g. There are 45 rows in this dataset)

@@

This problem and solution can be reduced to a paradigm of _best practices_ in
which reproducible, data-driven research is greatly simplified by R Markdown.
There are certainly [more thorough](https://rpubs.com/marschmi/105639) articles
on the topic, but we will focus on the highlights.

@@

We like to think that the sky is the limit when it comes to the reproducible
results that can be achieved using R Markdown, and are always excited to see
the impressive works that the open source community builds using this tool.

@@

Since our research in this workflow is entirely driven by data along the highway
of code, it makes sense to spend some time getting used to these tools. If we
make version control a part of our process, we get reproducible research up to a
moment in time. Further, since R Markdown consists of plaintext documents, we
acquire easy auditability of code that can be compared over time.
